Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
up section on modeling

\paragraph{Conclusion}

By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters. This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.

@@

Input data for the models are sourced from available building information, such as geometric dimensions, material properties, and occupancy schedules.
When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.

@@

\textbf{Nomenclature}\\
\begin{multicols}{2}
$\alpha$ : Absorption of a material.\hfill[-]\\
$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
$\Delta T$ : Temperature difference.\hfill[K]\\
$\epsilon$ : Emissivity of the surface.\hfill[-]\\
$\phi_{air}$ : Air heat flow.\hfill[W]\\
$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
$albedo$ : Reflective properties of the material.\hfill[-]\\
$A_z$ : Azimuth of the surface.\hfill[-]\\
$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
$H_s$ : Angular height of the sun.\hfill[-]\\
$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
$Met$ : Metabolic rate.\hfill[W]\\
$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
$S$ : Surface area.\hfill[m$^2$]\\
$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
\end{multicols}

>>>>

\paragraph{Conclusion} By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.

@@

Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.

Occupancy schedules are given as input to the models using reglementary occupancy.
We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).

This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.

@@

\section*{Nomenclature}

\begin{multicols}{2}
$\alpha$ : Absorption of a material.\hfill[-]\\
$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
$\Delta T$ : Temperature difference.\hfill[K]\\
$\epsilon$ : Emissivity of the surface.\hfill[-]\\
$\phi_{air}$ : Air heat flow.\hfill[W]\\
$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
$albedo$ : Reflective properties of the material.\hfill[-]\\
$A_z$ : Azimuth of the surface.\hfill[-]\\
$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
$H_s$ : Angular height of the sun.\hfill[-]\\
$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
$Met$ : Metabolic rate.\hfill[W]\\
$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
$S$ : Surface area.\hfill[m$^2$]\\
$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
\end{multicols}
